\documentclass{cv}

\newcommand\verticalPad{1.1cm}
\newcommand\horizontalpad{1.3cm}
\usepackage[left=\horizontalpad,top=\verticalPad,right=\horizontalpad,bottom=\verticalPad]{geometry}
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight}

\name{Jonathan Neidel}
\address{Born: {\em7. Aug 1997} in Berlin}
\address{Updated: \em{Mar 2024}}
\address{\email{cv@jneidel.com} \\ \github[jneidel] \\ \homepage[jneidel.com]{https://jneidel.com} \\ \linkedin[jneidel]}

\begin{document}

\begin{rSection}{Description}

  \newcommand\skillWidth{0.48}
  \begin{minipage}[t]{\skillWidth\linewidth}

I am a Backend/Fullstack Software Engineer apt at solving problems.
I started programming out of curiosity.
I fell in love with it when I saw the potential to solve a variety of problems for myself and others.
To me, programming is fundamentally about solving technical problems.

\medskip

My programming expertise could be grouped into two complementary parts. There is
the self-taught experimental hacking, driven by the desire to just make things
work. Which is elevated through the educated professional craftsmanship, guided
by the aspiration to produce clean code in structured cooperative manner.

\medskip

From the start I have always been working on personal projects. Building
everything from APIs, complete Webapps, small scripts and full-featured
command-line apps. The command-line especially is a passion of mine;
I do most of my work from the terminal and wrote my bachelor thesis about CLI
usability.
Through my long use of the completely self-configured Arch Linux I've also
acquired a deep understanding of Linux systems.

\medskip

  \end{minipage}
  \hfill
  \begin{minipage}[t]{\skillWidth\linewidth}

    On the professional side I have acquired my experience within the integrated Software
    Engineering workflow: Working in a ticket-based environment, coordinating with a
    team of developers, PMs, QA and other internal and external stakeholders.
    Delivering quality solutions and critical bug-fixes in a timely manner.
    Whenever possible, I tried to focus on improving the developer experience,
    technical documentation, environment and our processes.

    \medskip

    \textbf{Languages:}
    \begin{itemize}
      \item Web: JavaScript, TypeScript, SASS, React
      \item Backend/General purpose: Node.js (Express), PHP (Symfony), Python
    \end{itemize}

    \textbf{Databases:}
    \begin{itemize}
      \item SQL family
      \item MongoDB
    \end{itemize}

    \textbf{Tools \& Other:}
    \begin{itemize}
      \item Linux, Shell scripting
      \item Jest, Webpack, Eslint
      \item Git, Gitlab \& GitHub CI
      \item Docker, RabbitMQ
      \item Jira
    \end{itemize}

  \end{minipage}
\end{rSection}

\begin{rSection}{Education}

{\bf HTW Berlin}, Berlin \hfill {\em 2019 - 2023}\\
B.Sc in Applied Computer Science
  \hfill Grade: 2.0\\
  \href{https://github.com/jneidel/ba}{Thesis: Developing and evaluating methods for improving the usability of CLI apps}

\smallskip

{\bf Emil Molt Akademie}, Berlin \hfill {\em 2016 - 2018}\\
Fachabitur with a focus on economics
\hfill NC: 1.3

\end{rSection}

\begin{rSection}{Professional Experience}
  \textbf{\href{https://www.jobdirecto.com/}{Jobdirecto} - Fullstack Developer}
  \hfill {\em Feb 2023 - today}

  I came in and took over as the lead developer.
  The system and infrastructure was brought up-to-date; misguided components
  were refactored; technical documentation created and a new backlog of features agreed upon.

  \textbf{\href{https://www.endava.de/}{Endava} - Backend Developer}
  \hfill {\em Feb 2022 - today}

  Started as a intern and stayed on as a working student to do my bachelor thesis.
  After finishing uni, I assumed a developer position.
  See related projects below.

  \textbf{\href{https://buchhaltungsbutler.de/}{Buchhaltungsbutler} - Intern Business Development}
  \hfill {\em Feb - Aug 2017}

  A business internship where I had some opportunities to automate business tasks.
  Also, I also wrote complex excel macros for converting different account statements into our required formats.
\end{rSection}

\begin{rSection}{IT Projects}

  % \textbf{\href{}{}}
  % \hfill

  % \begin{list}{$\cdot$}{}
  %   \itemsep -0.5em \vspace{-0.5em}
  %   \smallskip
  %   \item
  % \end{list}

  \textbf{Endava: \href{https://tvthek.orf.at/}{Big PHP Project}}
  \hfill
  {\em Feb 2023 - today}

  PHP (Symfony, Sonata), Docker, RabbitMQ, PHPUnit, PHPStan, Webhooks, MariaDB (Doctrine)
  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Refactored the project for a major PHP version upgrade.
  \item Overhauled the local development setup.
  \item Specified and lead the development of a moderately-sized feature.
  \end{list}

  \textbf{\href{https://www.jobdirecto.com/}{Jobdirecto}}
  \hfill
  {\em Feb 2023 - today}

  React, Node.js (Express), MongoDB, Webpack, Stripe, Heroku, Jest
  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Introduced testing, technical documentation, backups and a staging environment.
  \end{list}


  \textbf{Endava: \href{https://github.com/jneidel/oraclett}{oraclett}}
  \hfill
  {\em Dec 2022 - today}

  Node.js (oclif), Github CI
  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Built a user-friendly CLI app that demonstrated the principles of my bachelor thesis.
  \end{list}

  \textbf{Endava: Soon@Endava}
  \hfill
  {\em Mar - Nov 2022}

  PHP (Symfony, Sonata), RabbitMQ, Docker
  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Implemented a full-fledged webapp based on Symfonys best-practices and a management CMS.
  \item Built a microservice that sends mail based on inputs from our message queue.
  \item Wrote user stories and tickets for the team. Assigned work and reviewed pull requests.
  \end{list}

  \textbf{Endava: Changelog Viewer}
  \hfill
  {\em Feb - Mar 2022}

  React, Docker, Gitlab CI
  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Built a parser and generator for producing an interactive version of a CHANGELOG.md file.
  \item Set-up automated dockerized deployments and using Gitlabs CI pipeline.
  \end{list}

  \textbf{\href{https://github.com/htw-kbe-jneidel/main}{Component based development - final project}}
  \hfill
  {\em Dec 2021 - Feb 2022}

  TypeScript, Node.js (Express), RabbitMQ, MongoDB (Mongoose), Github
  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Implemented a microservice architecture connected by message queue RPC calls.
  \item Wrote extensive technical documentation.
  \end{list}

  \textbf{\href{https://github.com/jneidel/what-to-do}{What to do}}
  \hfill
  {\em Nov 2020 - Apr 2021}

  Node.js (Express), Vue.js, MariaDB, Jest, supertest
  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Implementation of todo app functionality.
  \item Set-up deployment and integration.
  \end{list}

  \textbf{\href{https://github.com/vyvytn/avt}{DJ Tool}}
  \hfill
  {\em Oct 2020 - Jan 2021}

  JavaScript, Web Audio API, Node.js (Express), Vue.js
  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Implemented the underlying audio-logic.
  \item Provided a proxy to an external secured API.
  \end{list}

  \textbf{\href{https://github.com/jneidel/lock-me-out}{Lock Me Out}}
  \hfill
  {\em Jan - Mar 2019}

  TypeScript, Node.js (Express), GPG, Webpack, SASS, MongoDB, Eslint
  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Built a full-fledged webapp with serverside-rendering (SSR) and a CLI.
  \item Wrote a wrapper around GPG for using public-key crypto.
  \end{list}

  \textbf{\href{https://github.com/jneidel/dotfiles}{dotfiles}}
  \hfill
  {\em 2018 - today}

  Shell scripting, Linux, Shell, vim, tmux
  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Wrote 300+ shell utility scripts for a diverse range of automation tasks
  \end{list}

  \textbf{\href{https://github.com/jneidel/mangareader-dl}{mangareader-dl}}
  \hfill
  {\em 2018 - today}

  Node.js, CLI, Web Scraping, TDD, Jest, TypeScript
  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Built a full-featured managa scraping utility.
  \item Completely rebuilt the app in TypeScript with clean OOP structure in a test-driven fashion.
  \end{list}

  \textbf{\href{https://github.com/jneidel/setup-webpack}{Setup Webpack}}
  \hfill
  {\em 2018 - today}

  Webpack, JavaScript, SASS, npm package
  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Built an abstraction on top of webpack simplifying common use cases.
  \item Wrote extensive technical documentation and supported the package over the years.
  \end{list}

\end{rSection}

\begin{rSection}{Volunteering}

  \hfil  {\bf Maintaining AUR packages}
  \hfill
  {\em 2020 - today}

  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Maintenance of some \href{https://aur.archlinux.org/packages/?SeB=m&K=jneidel}{software packages} for my linux distribution.
  \end{list}

  {\bf Contributing to Open Source projects}
  \hfill
  {\em 2019 - today}

  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Maintenance of the most popular \href{https://github.com/agarrharr/awesome-cli-apps}{list of CLI apps} on Github.
  \item Submission of bug reports and patches to software that I'm using.
  \end{list}

  {\bf Organizer of the Berlin FreeCodeCamp Meetup}
  \hfill
  {\em 2018 - 2019}

  \begin{list}{$\cdot$}{}
  \itemsep -0.5em \vspace{-0.5em}
    \smallskip
  \item Hosted a weekly meetup for aspiring developers, where I was the go-to person for technical questions.
  \end{list}

\end{rSection}

\begin{rSection}{Languages}
  \begin{minipage}[l]{0.48\linewidth}
    {\bf German:} native
  \end{minipage}
  \begin{minipage}[l]{0.48\linewidth}
    {\bf English:} fluent \hfill
  \end{minipage}
\end{rSection}

\begin{rSection}{Interests}

  Outside of programming, this is some of what I spend my time on:

  {\bf Writing:}
  While working on my bachelor thesis I realized that I actually quite liked
  writing in a structured way.
  I've channeled that into \href{https://jneidel.com/blog/}{my blog}, where I
  irregularly write comprehensive guides on topics that I have recently delved
  into.

  {\bf Spending time in nature:}
  Being closer to ``real" nature was one of my reasons for moving away from Berlin.
  I highly value my 3 min forest access and make use of it regularly.

  {\bf Being of service:}
  I always take the time to be a good friend/son/brother/husband in whatever
  shape that might take.
  I have for example recently deployed my Linux skillset to provide them with some services on my home server.

  {\bf Working on my personal development:}
  By improving myself and the systems/processes/habits that make up my life.
  I spend my time reflecting, planning, researching, reading and then applying what I
  learned.

  Some of 2023's outcomes were:
  \begin{itemize}
    \item Created a note-taking system for structuring and making sense of all the
      information that I come into contact with.
    \item Improved our diet by increasing the amount of raw vegetables we
      consume, cutting almost all products with industrial sugar in them and picking up
      fermentation and bread baking.
    \item Further improved my sleep by sticking to a fixed schedule, providing a cooler
      environment and emphasizing wind-down time in the evening.
    \item Created the processes around a double-entry bookkeeping system for budgeting and tracking my expenses.
    \item Improved my soft skills and intangibles immeasurably.
  \end{itemize}

\end{rSection}
\end{document}
